Bringing the Power of eBPF to Open vSwitch

### 2018-10-24 paper.tex
fix FIFO / FILO

\subsubsection{Memory Management and Locks}\label{memorym}
For every stage of optimizations, we use Linux perf extensively, e.g., perf stat
and perf record/report.  With the above new design, we observe the new bottleneck
is at the umempool APIs we introduce, as well as at the
packet metadata allocation, struct dp\_packet, for every received packet.
We introduce two major APIs, umem\_elem\_get(), which gets N free element from the
umempool, and umem\_elem\_put(), which places back the free umem buffer to
the umempool, similar to the concept of producer (put) and consumer (get).
We implemented three different data structures of umempool as below
to compare their performance.
\begin{itemize}
\item FIFO-list\_head: We reversed first 8-byte of the umem buffer as a next pointer,
pointing to the next available element in umempool, and implement FIFO access get/set
APIs. The list\_head pointer always points to the first available umem element.
\item FILO-ptr\_ring: Similar to Linux kernel's ptr\_ring, an array of elements are
allocated in continuous memory region.
Consumer takes elements from the tail pointer and when placing back, producer, puts
them into where head pointer points to.
\item FIFO-ptr\_array: Similar to Linux kernel's skb\_array~\cite{skbarray},
an array of elements are allocated
in continuous memory region, but both consumer and producer take elements
from beginning of the array.
\end{itemize}

@@

With the above design change, we found that using the FIFO-ptr\_array in section~\ref{memorym} with
separate from packet buffer design yields the best performance. Largely due to both data structures
have better spatial locality and more batching friendly, when all data are allocated together.
For example, setting up 32 packet metadatas in an array definitely incurs
less cache misses than setting up in 32 elements in umem.
And getting 32 free umem elements from ptr\_array has similar benefits.
With the above decision, the OVS rxdrop shows around $19Mpps$, closed
to the baseline xdpsock rxdrop performance.

>>>>

\subsubsection{Memory Management and Locks}\label{memorym}
For every stage of optimizations, we use Linux perf extensively, e.g., perf stat
and perf record/report.  With the above new design, we observe the new bottleneck
is at the umempool APIs we introduce, as well as at the
packet metadata allocation, struct dp\_packet, for every received packet.
We introduce two major APIs, umem\_elem\_get(), which gets N free element from the
umempool, and umem\_elem\_put(), which places back the free umem buffer to
the umempool, similar to the concept of producer (put) and consumer (get).
We implemented three different data structures of umempool as below
to compare their performance.
\begin{itemize}
\item FILO-list\_head: We reversed first 8-byte of the umem buffer as a next pointer,
pointing to the next available element in umempool, and implement FIFO access get/set
APIs. The list\_head pointer always points to the first available umem element.
\item FIFO-ptr\_ring: Similar to Linux kernel's ptr\_ring, an array of elements are
allocated in continuous memory region.
Consumer takes elements from the tail pointer and when placing back, producer, puts
them into where head pointer points to.
\item FILO-ptr\_array: Similar to Linux kernel's skb\_array~\cite{skbarray},
an array of elements are allocated
in continuous memory region, but both consumer and producer take elements
from beginning of the array.
\end{itemize}

@@

With the above design change, we found that using the FILO-ptr\_array in section~\ref{memorym} with
separate from packet buffer design yields the best performance. Largely due to both data structures
have better spatial locality and more batching friendly, when all data are allocated together.
For example, setting up 32 packet metadatas in an array definitely incurs
less cache misses than setting up in 32 elements in umem.
And getting 32 free umem elements from ptr\_array has similar benefits.
With the above decision, the OVS rxdrop shows around $19Mpps$, closed
to the baseline xdpsock rxdrop performance.
